---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE)
```


#Naive Bayes

In machine learning, naive Bayes classifiers are a family of simple probabilistic classifiers based on applying Bayes' theorem with strong (naive) independence assumptions between the features.

Naive Bayes has been studied extensively since the 1950s. It was introduced under a different name into the text retrieval community in the early 1960s, and remains a popular (baseline) method for text categorization, the problem of judging documents as belonging to one category or the other (such as spam or legitimate, sports or politics, etc.) with word frequencies as the features. With appropriate preprocessing, it is competitive in this domain with more advanced methods including support vector machines. It also finds application in automatic medical diagnosis.

Naive Bayes classifiers are highly scalable, requiring a number of parameters linear in the number of variables (features/predictors) in a learning problem. Maximum-likelihood training can be done by evaluating a closed-form expression, which takes linear time, rather than by expensive iterative approximation as used for many other types of classifiers.

In the statistics and computer science literature, Naive Bayes models are known under a variety of names, including simple Bayes and independence Bayes. All these names reference the use of Bayes' theorem in the classifier's decision rule, but naive Bayes is not (necessarily) a Bayesian method; Russell and Norvig note that "[naive Bayes] is sometimes called a Bayesian classifier, a somewhat careless usage that has prompted some Bayesians to call it the idiot Bayes model."

```{r warning=FALSE}

 library(caret)
 library(kernlab)
 data(spam)
 inTrain <- createDataPartition(y= spam$type,p=0.85,list=FALSE)
 training <- spam[inTrain,]
 testing <- spam[-inTrain,]
 dim(training)
#[1] 3912 58
 
 set.seed(32343)
 modelFit <- train(type~.,data=training,method="nb")
#There were 50 or more warnings (use warnings() to see the first 50)
 
 prediction <- predict(modelFit,newdata=testing)
#There were 50 or more warnings (use warnings() to see the first 50)
 
 confusionMatrix(prediction,testing$type)



```

Source: http://trymachinelearning.com/machine-learning-algorithms/bayesian-machine-learning/naive-bayes/